Supplementary material for ``Screening Sinkhorn Algorithm for Regularized Optimal Transport''

### 2019-05-22 tex/v3/section_5_numeric_expes.tex
update

Figure \ref{fig:wda} presents the average gain (over $30$ trials) in computational time we get as the number of examples evolve and for different decimation factors of the \emph{Screenkorn} problem.
Analysis of the quality of the subspace have been deported to the supplementary material (see Figure 1), but we can remark a small loss of performance of \emph{Screenkhorn} for the toy problem, while
for MNIST, accuracies are equivalent regardless of the decimation factor.  We can note
that for the minimal gains are respectively $2$ and $4.5$ for the toy and MNIST problem
whereas the maximal gain for $4000$ samples is slightly larger than an order of magnitude.

@@

For the optimal transport based domain adaptation problem, we have considered the
OTDA with $\ell_{0.5,1}$ group-lasso regularizer that helps in exploiting available labels in the source domain. The problem is solved using an majorization-minimization approach 
for handling the non-convexity of the problem. Hence, at each iteration, a Sinkhorn/\emph{Screenkhorn} has to be computed. As a domain-adaptation problem, we have
used a MNIST to USPS problem in which features have been extracted from the
feature extractor of an domain adversarial neural networks \citep{ganin2016domain} before full convergence of the networks (so as to leave room for OT adaptation). 
Figure \ref{fig:otda} reports the gain in running time for $2$ different values
of the group-lasso regularizer hyperparameter, while the curves of performances are
reported in the supplementary material. We can note that for all the  \emph{Screenkhorn} with different decimation factors, the gain in computation goes from a factor of $4$ to $12$, while accuracies are somewhat equivalent.

>>>>

Figure \ref{fig:wda} presents the average gain (over $30$ trials) in computational time we get as the number of examples evolve and for different decimation factors of the \emph{Screenkorn} problem.
Analysis of the quality of the subspace have been deported to the supplementary material (see Figure~\ref{fig:wda_gain}), but we can remark a small loss of performance of \emph{Screenkhorn} for the toy problem, while
for MNIST, accuracies are equivalent regardless of the decimation factor.  We can note
that for the minimal gains are respectively $2$ and $4.5$ for the toy and MNIST problem
whereas the maximal gain for $4000$ samples is slightly larger than an order of magnitude.

@@

For the OT based domain adaptation problem, we have considered the
OTDA with $\ell_{0.5,1}$ group-lasso regularizer that helps in exploiting available labels in the source domain. The problem is solved using an majorization-minimization approach 
for handling the non-convexity of the problem. Hence, at each iteration, a Sinkhorn/\emph{Screenkhorn} has to be computed. As a domain-adaptation problem, we have
used a MNIST to USPS problem in which features have been extracted from the
feature extractor of an domain adversarial neural networks \citep{ganin2016domain} before full convergence of the networks (so as to leave room for OT adaptation). 
Figure \ref{fig:otda} reports the gain in running time for $2$ different values
of the group-lasso regularizer hyperparameter, while the curves of performances are
reported in the supplementary material. We can note that for all the  \emph{Screenkhorn} with different decimation factors, the gain in computation goes from a factor of $4$ to $12$, while accuracies are somewhat equivalent.
